Theories of deliberated choice

### 2023-10-22 simple.tex
Applying coro

  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:unfals}
  Given $\ar \neq \ar' \in \allargs$,
  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  $\hist \ileadstog[j] \phi \land [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:unfals} concludes.
\end{example}
\begin{example}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

@@

\begin{corollary}
  \label{th:corffals}
  A claim $C$ is falsifiable iff $\forall f \in \left(C^\subseteq\right)^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
\end{corollary}
\begin{corollary}
  \label{th:corffalsdom}
  A claim $C$ is falsifiable iff $\forall f \in \cup_{O \in \allpriobss} \set{\set{O} × (P^O \cap C^\subseteq)} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
  \[\cup_{O \in \allpriobss} f(O) \in C.\]
\end{corollary}
\begin{corollary}
  \label{th:veryunfals}
  Any non-trivial claim $C$ satisfying $\forall O \in \allpriobss, {\allleadstog} \in \allleadstos: \restr{\allleadstog}{O} \in C^\subseteq$ is not falsifiable.
\end{corollary}
\begin{proof}
  Pick any ${\allleadstog} \notin C$.
  Define $f$ as $\forall O \in \allpriobss: f(O) = \restr{\allleadstog}{O}$.
  Observe that $\cup_{O \in \allpriobss} f(O) = {\allleadstog}$ and hence $\cup_{O \in \allpriobss} f(O) \notin C$.
  Apply \cref{th:corffalsdom}.
\end{proof}

\begin{example}
  Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.
\end{example}

>>>>

  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:disj}
  Given $\ar \neq \ar' \in \allargs$,
  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $S_θ \cap C ≠ \emptyset$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  \label{ex:partlyU}
  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
  $\hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:disj} concludes.
\end{example}
\begin{example}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}
  Consider any $\ar_1 ≠ \ar_2 \in \allargs$, $p ≠ p' \in P$ and any ${\allleadstog^1}, {\allleadstog^2}$ such that $(\ar_1) \ileadstog^1 p$ and $(\ar_1) \ileadstog^2 p'$.
  The claim $C = \set{{\allleadstog^1}, {\allleadstog^2}}$ is unfalsifiable.

@@

\begin{corollary}
  \label{th:corffals}
  A claim $C$ is falsifiable iff $\forall f \in \left(C^\subseteq\right)^{\allpriobss} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
  \[\cup_{O \in \allpriobss} \restr{f(O)}{O} \in C.\]
\end{corollary}
\begin{corollary}
  \label{th:corffalsdom}
  A claim $C$ is falsifiable iff $\forall f \in \cup_{O \in \allpriobss} \set{\set{O} × (P^O \cap C^\subseteq)} \suchthat \forall O, O' \in \allpriobss: \restr{f(O)}{O \cap O'} = \restr{f(O')}{O \cap O'}$:
  \[\cup_{O \in \allpriobss} f(O) \in C.\]
\end{corollary}
\begin{corollary}
  \label{th:veryunfals}
  Any non-trivial claim $C$ satisfying $\Theta \subseteq C^\subseteq$ is not falsifiable.
\end{corollary}
\begin{proof}
  Pick any ${\allleadstog} \notin C$.
  Per hypothesis, $\forall O \in \allpriobss$: $\restr{\allleadstog}{O} \in C^\subseteq$.
  Define $f$ as $\forall O \in \allpriobss: f(O) = \restr{\allleadstog}{O}$.
  Observe that $\cup_{O \in \allpriobss} f(O) = {\allleadstog}$ and hence $\cup_{O \in \allpriobss} f(O) \notin C$.
  Apply \cref{th:corffalsdom}.
\end{proof}

\begin{example}
  Considering again \cref{ex:bigor}, by \cref{th:veryunfals}, we see that $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$ is not falsifiable.

  Similarly, considering again \cref{ex:disj}, given $\ar \neq \ar' \in \allargs$,
  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable, by \cref{th:veryunfals}.

  Turning to \cref{ex:partlyU},
  given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
  $C = \set{{\allleadstog} \suchthat \hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]}$ is not falsifiable but \cref{th:veryunfals} is not applicable.
  Observe that $C^\subseteq = \set{R \in I × \allhists × P \suchthat [(j, \hist) \in R^{-1}(P) \implies (j, \hist, \phi) \in R] \land \forall i: [(i, (\ar)) \in R^{-1}(P) \land (i, (\ar')) \in R^{-1}(P)] \implies [(i, (\ar), \phi) \in R \land (i, (\ar'), \phi) \in R]}$.
  Pick any $\allleadstog$ satisfying $\hist \ileadstog[j] \phi$ and $\exists i \suchthat (\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  The definition of non-falsifiability applies: pick any $\theta \subseteq {\allleadstog}$, we have $\theta \in C^\subseteq$ as $(j, \hist, \phi)$ is compatible with $\theta$ and the other condition excludes nothing in $\Theta$.
  We can apply Thm 4 similarly: given any $O$, we have $\restr{\allleadstog}{O} \in C^\subseteq$.

  We should be able to apply a corollary similarly.
  Given any $O$, define $f(O) = \restr{\allleadstog}{O}$ and observe that $f(O) \in C^\subseteq$ although $\cup_{O \in \allpriobss} f(O) \notin C$.
\end{example}

TODO continue here (finish examples above).
